Data Management for LSST Special Programs

### 2023-10-19 ap_spcs.tex
change appendix title
fix typo

\section{Scenarios for Processing Data from Special Programs}\label{sec:spcs}

@@

Step 4. Regular processing for inclusion in WFD program data products. \\
Every year, each $2\times15$ second standard visit is reprocessed by the DIA data release pipelines
and the results are included alongside WFD program data in the relevant DIA data products
(e.g., processed visit images, difference images, associated source catalogs).
In the first year after the Special Program is executed,
Rubin Data Management finds that 10% of the standard visits from this Special Program
had coordinates and image quality that help improve uniformity of the all-sky coadd,
and so they are included.
In later years, this fraction decreases (remember, this is \emph{hypothetical}).
In all data releases, any and all processed images and catalog sources that originate in visits from this Special Program
have the same region and program labels, e.g., ``SP-OSSO".

>>>>

\section{Hypothetical Scenarios}\label{sec:spcs}

@@

Step 4. Regular processing for inclusion in WFD program data products. \\
Every year, each $2\times15$ second standard visit is reprocessed by the DIA data release pipelines
and the results are included alongside WFD program data in the relevant DIA data products
(e.g., processed visit images, difference images, associated source catalogs).
In the first year after the Special Program is executed,
Rubin Data Management finds that 10\% of the standard visits from this Special Program
had coordinates and image quality that help improve uniformity of the all-sky coadd,
and so they are included.
In later years, this fraction decreases (remember, this is \emph{hypothetical}).
In all data releases, any and all processed images and catalog sources that originate in visits from this Special Program
have the same region and program labels, e.g., ``SP-OSSO".
